### 2020-03-08 draft_ABP.tex
merge from overleaf

We shall list a few results about permutahedra which shall be useful for later purposes: 
\begin{itemize}
\item {\bf Coordinate independence:} The combinatorial structure of the permutahedron ${\mathscr P_n} (x_1, \cdots, x_{n+1}) $ does not depend on $ x_1, \cdots, x_{n+1} $ as long as all these are distinct. Henceforth  we will choose $ \{x_1, \cdots, x_{n+1}\} = \{0,1,\cdots,n \} := [0,n ]$. \\
\item {\bf Facial Structure:} The $(n-k)$ faces of ${\mathscr P_n}$ are in an $1-1$ correspondence with the decomposition of $[0,n]$ into $k$ parts. More precisely, for each $(S_1,\cdots,S_k)$ with $S_i \neq \emptyset ~ \forall i$ and $[0,n] = S_1 \sqcup \cdots \sqcup S_k$ the corresponding face $\pi_{S_1,\cdots,S_k}$ has vertices which are permutations such that the entries $ \{x_i | i \in S_1 \}$ are largest $|S_1|$ numbers in $[0,n]$, $\{x_i | i \in S_2 \}$ are largest $|S_2|$ numbers in $[0,n]$ and so on.

@@

It follows from above that ${\mathscr P_n}$ has $2^{n+1} -2$ facets corresponding to all the non-empty proper subsets of $I$ for which we have a decomposition $[0,n] = S \sqcup S^c$ and the facets are isomorphic to one of the following product of lower dimensional permutahedra  $ \{ {\mathscr P_{n-1}}, {\mathscr P_{n-2}} \times A_1, \cdots ,{\mathscr P_{\lfloor{n/2 \rfloor}}} \times {\mathscr P_{n-1-\lfloor n/2 \rfloor}}  \} $\footnote {More generally the number of $(n-k)$ facets of ${\mathscr P_n}$ is $ k! S(n,k)$ where $S(n,k)$ is the Stirling number of the second kind which counts the number $k$ partitions of  $I$ and there are $p(n+1,k)$ types where $p(n+1,k)$ is the number of $k$ partitions of $(n+1)$.}.

@@

A  generalised permutahedron is obtained by parallel translation of facets of the usual permutahedron it is parametrized  by a collection $\{ z_I\}$ of $2^{n+1}-1$ coordinates, for non-empty sets of $I \subset [0,n] $
 \bea \label{genperm_defi}
 P_n^z(\{ z_I \}) = \left \{ (t_0 , t_1, \cdots , t_{n}) \in \mathbb{R}^{n+1} | \sum_{i=0}^{n} t_i = z_{[0,n]},~ \sum_{i \in I} t_i \geq z_I, {\rm for ~subsets} ~I  \right  \}
 \eea
 (a better notation for generalized permutahedron ??)

 If $z_I =z_J$ whenever $|I| =|J|$, then  $ P_n^z(\{ z_I \})$ is the usual permutahedron. 
 \begin{itemize}
 \item The combinatorial structure of the generalised permutahedron depends only on the set $B$ of nonemepty subsets $I \subset [0,n]$ such that $y_I \geq 0$ which is called the {\it building set}. To describe the combinatorial structure we need the notion of {\it Nested complex} which we shall define now.
 \end{itemize}

\subsection*{Nested Complex}
If $B$ additionally satisfies the following:
\begin{compactenum}[\quad (1)]
    \item If $I,J \in B$ and $I \cap J \neq \phi $, then $I \cup J \in B$.
    \item $B$ contains all singletons $\{ i\}$ for $i \in S$.
\end{compactenum}
A subset $N$ in the building set $B$ is called a {\it nested set} if it satisfies the following conditions:
\begin{compactenum}[\quad (1)]
    \item For any $I,J \in N$, we either have $I \subset J$ or $J\subset I$ or $I$ and $J$ are disjoint.
    \item For any collection of $k \geq 2$ disjoint subsets $J_1,J_2,\cdots, J_k \in N$ their union $J_1 \cup \cdots \cup J_k$ is not in B.
    \item $N$ contains all maximal elements of $B$.
\end{compactenum}
The {\it nested complex} $\mathcal{N}(B)$ is defined as the poset of the set of all nested sets in $B$ ordered by inclusion.

 \begin{itemize}
\item {\bf Minkowski decomposition:} Let, $\Delta_{[0,n]} = {\rm ConvexHull}(e_1,\cdots,e_n)$ be the standard coordinate simplex in $\mathbb{R}^{n+1}$. For any $I \subset [0,n] $ let $\Delta_I ={\rm ConvexHull(e_i~|~i\in I)}$ denote the face of the $\Delta_{[0,n]}$. The polytope $P_n^y(\{y_I \})$ obtained as the Minkowski sum of simplices $\Delta_I$ scaled by  parameters $y_I \geq 0$ for all nonempty subsets $I \subset [0,n]$
 \bea
 P_n^y(\{y_I \})= \sum_{I \subset[0,n]} y_I . \Delta_I  \nonumber
 \eea
is the generalised permutahedron $P_n^z(\{z_I \})$ if $z_I = \sum_{J \subset I} y_J  ~{\rm for~all~nonempty}~I \subset [0,n]$.
\footnote{Not all generalised permutahedra cannot be written as Minkowski sum of coordinate simplices. We shall restrict ourselves to the large class of generalised permutahedra which admit such a realisation which are called Nestohedra.}

\item {\bf Facial structure:} Let us assume that the set $B$ associated with a generalised permutahedron $P_n^{y}$ is a building set on $[0,n]$. Then the poset of faces $P_n^{y}$ ordered by reverse inclusion is isomorphic to the nested complex $\mathcal{N}(B)$.

For each decomposition $[0,n]=  \sqcup_{I \subset N } S_I $ where $S_I$ are non-empty, the face $P_N$ of $P_n^{y}(y_I)$ associated with the nested set $N \in \mathcal{N}(B)$ is:
\bea
P_N = \sum_{{J \subset B}\atop{J \cap S_I \neq \emptyset}} y_{J} \Delta_{J \cap S_I}
\eea
\end{itemize}
\section*{Braid arrangement}
The braid arrangement in $\mathbb{R}^{n+1}$ consists of $\left({n}\atop{2}\right)$ hyperplanes 
\bea
z_i =z_j ~~{\rm for ~ all}~~0 \leq i<j \leq n
\eea

In summary the above results imply that we can look at any collection of subsets of $[0, n]$ which form a building set $B$ and associate  coordinate simplex $\Delta_I$ for each $I \in B$ and resulting Minkowski sum with positive weights $y_I$ generates a generalised permutahedron associated with the building set. Further, the number of facets of the generalised permutahedron just correspond to the set of all non-singlet elements in $B$.

We shall set $x_0 =1$ from now on. Since, the number of singlets correspond to the dimension of the generalised permutahedron this implies that:

@@

(3) If $B$ corresponds to all the non empty subsets of $[0,n]$ and $Y_I =y_{|I|}$ i.e., the variables $Y_I$ are equal for all subsets of the same cardinality, then $P_n({\bf Y})$ is the usual permutahedron $P_n$.

(4)If $B=\{ [i,j] | 1\leq  i \leq j \leq n\}$ is the set of consecutive intervals, then $P_n({\bf Y})$ is the associahedron.

(5) If $B=\{ [1,i] \cup [j,n] | 1\leq  i \leq j \leq n\}$ is the set of cyclic intervals, then $P_n({\bf Y})$ is the Cyclohedron.

The cases (4) and (5) will be considered in section (3.2). In this section we shall restrict ourselves to the permutahedron example ${\mathscr P_n}$.  
\subsection{Natural stringy integrals with linear factors}

@@

Within all generalized permutahedrons, the original permutahedron is quite simple
and important because any other generalized permutahedron can be degenerated from
permutahedron by setting some $S_I$ to be zero.
The building set of the $n$-dimensional permutahedron $\mathscr P_n$ is 
the set of all non-empty subsets of $[0,n]$. AHBY conditions can be solved from 
eq.\eqref{GPfacet}
\[
	S_I = (-1)^{|I|+1}\sum_{i\in I} S_i,
\]
for all non-empty subsets $I \subset [0,n]$ which are not singlets.
To get $u$-equations, we should solve $S_J$ by $F_J$ from eq.\eqref{GPfacet}, the 
solution for permutahedron $\mathscr P_n$ is 
\begin{equation}\label{SinF}
	S_I=\sum_{J\neq \varnothing,J\subset I} (-1)^{|J|-|I|}F_J,
\end{equation}
then
\[
	\prod_{I\neq \varnothing,I\subset [0,n]}u_I^{F_I}=
	\prod_{I\neq \varnothing,I\subset [0,n]}x_I^{S_I}=
	\prod_{\varnothing\neq J\subset I\subset [0,n]}
	x_I^{(-1)^{|J|-|I|}F_J}=
	\prod_{J\neq \varnothing,J\subset [0,n]}
	\prod_{I\supset J}(x_I^{(-1)^{|J|-|I|}})^{F_J}
\]
gives that
\[
	u_I=\prod_{J\supset I}x_J^{(-1)^{|I|-|J|}}.
\]
For example, the $u$-variables of $\mathscr P_2$ are
\[
	u_{1}  = \frac{x_1 x_{123}}{x_{12}x_{13}},\quad 
	u_{2}  = \frac{x_2 x_{123}}{x_{12}x_{23}},\quad
	u_{3}  = \frac{x_3 x_{123}}{x_{13}x_{23}},\quad
	u_{12} = \frac{x_{12}}{x_{123}},\quad 
	u_{13} = \frac{x_{13}}{x_{123}},\quad
	u_{23} = \frac{x_{23}}{x_{123}}.
\]
They satisfy the following equtions
\begin{align*}
	&1-u_{1}=u_{2} u_{3} u_{23}^2,
	1-u_{2}=u_{1} u_{3} u_{13}^2,
	1-u_{3}=u_{1} u_{2} u_{12}^2,\\
	&1-u_{12}=u_{3} u_{13} u_{23},
	1-u_{13}=u_{2} u_{12} u_{23},
	1-u_{23}=u_{1} u_{12} u_{13}.
\end{align*}
We will discuss these $u$-equations in the next subsection.

@@

{\bf argue in general to have binary geometries we must have $1-u=\prod u' p(\{u\})$ with $p(u=0)=1$, conjecture that this is true fo ALL gen. perm. Show it for gen. perm. more examples?}

@@

In the above, we have shown that the binary geometries exist for permutohedra even through the $u$ equtions are not perfect and conjecture that such binary geometries exist for generalized permutohedra. In the remainder of this section, we will give more example on such binary geometries without perfect $u$ equtions.

@@

the $u$ variables are 
\begin{align}
   &u_{1}=\frac{x_{1}x_{123}}{x_{12}x_{13}} \:, \quad  u_{2}=\frac{x_{2}x_{123}}{x_{12}x_{23}} \:,  \quad 
   u_{3}=\frac{x_{3}x_{134}x_{234}x_{123}}{x_{34}x_{13}x_{23}x_{1234}} \:, \quad 
   u_{4}=\frac{x_{4}}{x_{34}} \\
   &u_{12}=\frac{x_{12}}{x_{123}} \:, \quad u_{13}=\frac{x_{13}x_{1234}}{x_{134}x_{123}} \:,\quad 
   u_{23}=\frac{x_{23}x_{1234}}{x_{123}x_{234}} \:, \quad u_{34}=\frac{x_{34}x_{1234}}{x_{134}x_{234}} \\
   &u_{123}=\frac{x_{123}}{x_{1234}} \:, \quad u_{134}=\frac{x_{134}}{x_{1234}} \:, \quad 
   u_{234}=\frac{x_{234}}{x_{1234}}
\end{align}
The $u$ equations are
\begin{align}
   &1-u_{1}=u_{2}u_{3}u_{23}^{2}u_{34}u_{234}^{2} \:, \\
   &1-u_{2}=u_{1}u_{3}u_{13}^{2}u_{34}u_{123}^{2} \:, \\
   &1-u_{3}= u_{1}u_{2}u_{4}u_{12}^{2}(1+u_{3}u_{13}u_{23}u_{34}u_{123}u_{134}u_{234}) \:, \\
   &1-u_{4}=u_{3}u_{13}u_{23}u_{123}  \:, \\
   &1-u_{12} =u_{3}u_{13}u_{23}u_{34}u_{134}u_{234} \:, \\
   &1-u_{13} =u_{2}u_{4}u_{12}u_{23}u_{34}u_{234}^{2} \:, \\
   &1-u_{23}= u_{1}u_{4}u_{12}u_{13}u_{34}u_{134}^{2} \:, \\
   &1-u_{34}= u_{1}u_{2}u_{12}^{2}u_{13}u_{23}u_{123}^{2} \:, \\
   &1-u_{123}=u_{4}u_{34}u_{134}u_{234} \:, \\
   &1-u_{134}=u_{2}u_{12}u_{23}u_{123}u_{234} \:, \\
   &1-u_{234}=u_{1}u_{12}u_{13}u_{123}u_{134} \:, 
\end{align}

\section{Configuration spaces with perfect $u$-equations from degenerating $A_n$ and $B_n$}
In this section we shall consider some degenerations of $A_n$ and $B_n$ and show that these form an infinite class of examples of binary geometries with perfect $u$-equations. To do this we shall use the fact that both $A_n$ and $B_n$ are generalised permutahedra and can be realised as a Minkowski sum of coordinate simplices.

@@

>>>>

We shall list a few results about permutahedra which shall be useful for later purposes: 
\begin{itemize}
\item {\bf Parameter independence:} The combinatorial structure of the permutahedron ${\mathscr P_n} (x_1, \cdots, x_{n+1}) $ does not depend on $ x_1, \cdots, x_{n+1} $ as long as all these are distinct. Henceforth  we will choose $ \{x_1, \cdots, x_{n+1}\} = \{0,1,\cdots,n \} := [0,n ]$. \\
\item {\bf Facial Structure:} The $(n-k)$ faces of ${\mathscr P_n}$ are in an $1-1$ correspondence with the decomposition of $[0,n]$ into $k$ parts. More precisely, for each $(S_1,\cdots,S_k)$ with $S_i \neq \emptyset ~ \forall i$ and $[0,n] = S_1 \sqcup \cdots \sqcup S_k$ the corresponding face $\pi_{S_1,\cdots,S_k}$ has vertices which are permutations such that the entries $ \{x_i | i \in S_1 \}$ are largest $|S_1|$ numbers in $[0,n]$, $\{x_i | i \in S_2 \}$ are largest $|S_2|$ numbers in $[0,n]$ and so on.

@@

It follows from above that ${\mathscr P_n}$ has $2^{n+1} -2$ facets corresponding to all the non-empty proper subsets of $[0,n]$ for which we have a decomposition $[0,n] = S \sqcup S^c$ and the facets are isomorphic to one of the following product of lower dimensional permutahedra  $ \{ {\mathscr P_{n-1}}, {\mathscr P_{n-2}} \times A_1, \cdots ,{\mathscr P_{\lfloor{n/2 \rfloor}}} \times {\mathscr P_{n-1-\lfloor n/2 \rfloor}}  \} $\footnote {More generally the number of $(n-k)$ facets of ${\mathscr P_n}$ is $ k! S(n,k)$ where $S(n,k)$ is the Stirling number of the second kind which counts the number $k$ partitions of  $I$ and there are $p(n+1,k)$ types where $p(n+1,k)$ is the number of $k$ partitions of $(n+1)$.}.

@@

A  generalised permutahedron is obtained by parallel translation of facets of the usual permutahedron it is parametrized  by a collection $\{ z_I\}$ of $2^{n+1}-1$ coordinates, for non-empty sets of $I \subset [0,n] $
 \bea \label{genperm_defi}
 P_n^z(\{ z_I \}) = \left \{ (t_0 , t_1, \cdots , t_{n}) \in \mathbb{R}^{n+1} | \sum_{i=0}^{n} t_i = z_{[0,n]},~ \sum_{i \in I} t_i \geq z_I, {\rm for ~subsets} ~I  \right  \}
 \eea
 If $z_I =z_J$ whenever $|I| =|J|$, then  $ P_n^z(\{ z_I \})$ is the usual permutahedron.

 Unlike the permutahedron not all generalised permutahedra can be represented as a Minkowski sum of co-ordinate simplices. We shall restrict ourselves to the large class of generalised permutahedra which admit such a realisation which are called Nestohedra which we denote by ${\mathscr N}$. Throughout the paper we shall mean Nestohedra whenever we refer to generalized permutahedra unless stated otherwise.
 \begin{itemize}
 \item {\bf Minkowski decomposition:} Let, $\Delta_{[0,n]} = {\rm ConvexHull}(e_1,\cdots,e_n)$ be the standard coordinate simplex in $\mathbb{R}^{n+1}$. Then we have:
  \bea
{\mathscr N_n}^y(\{y_I \})= \sum y_I . \Delta_I  \nonumber
 \eea
 for some collection of subsets $I \in [0,n]$
 \end{itemize}
  \begin{itemize}
 \item{\bf Parameter Independence:} The combinatorial structure of the generalised permutahedron ${\mathscr N_n({y_I})}$ is independent of the parameters $y_I$ and depends only on the collection of subsets $I \in [0,n]$ called the  building set $B$.  \end{itemize}
A collection of non-empty subsets of $[0,n]$ is called a building set $B$ if it satisfies the following:
\begin{compactenum}[\quad (1)]
    \item If $I,J \in B$ and $I \cap J \neq \phi $, then $I \cup J \in B$.
    \item $B$ contains all singletons $\{ i\}$ for $i \in S$.
\end{compactenum}
To describe the combinatorial structure we need the notion of {\it Nested complex} which we shall define now.
\subsection*{Nested Complex}
A subset $N$ in the building set $B$ is called a {\it nested set} if it satisfies the following conditions:
\begin{compactenum}[\quad (1)]
    \item For any $I,J \in N$, we either have $I \subset J$ or $J\subset I$ or $I$ and $J$ are disjoint.
    \item For any collection of $k \geq 2$ disjoint subsets $J_1,J_2,\cdots, J_k \in N$ their union $J_1 \cup \cdots \cup J_k$ is not in B.
    \item $N$ contains all maximal elements of $B$.
\end{compactenum}
The {\it nested complex} $\mathcal{N}(B)$ is defined as the poset of the set of all nested sets in $B$ ordered by inclusion.

 \begin{itemize}

\item {\bf Facial structure:} Let us assume that the set $B$ associated with a generalised permutahedron ${\mathscr N_n}^{y}$ is a building set on $[0,n]$. Then the poset of faces ${\mathscr N_n}^{y}$ ordered by reverse inclusion is isomorphic to the nested complex $\mathcal{N}(B)$.

For each decomposition $[0,n]=  \sqcup_{I \subset N } S_I $ where $S_I$ are non-empty, the face $P_N$ of ${\mathscr N_n}^{y}(y_I)$ associated with the nested set $N \in \mathcal{N}(B)$ is:
\bea
P_N = \sum_{{J \subset B}\atop{J \cap S_I \neq \emptyset}} y_{J} \Delta_{J \cap S_I}
\eea
\end{itemize}

In summary the above results imply that we can look at any collection of subsets of $[0, n]$ which form a building set $B$ and associate  coordinate simplex $\Delta_I$ for each $I \in B$ and resulting Minkowski sum with positive weights $y_I$ generates a generalised permutahedron associated with the building set. Further, the number of facets $N$ of the generalised permutahedron just corresponds to the set of all elements in $B$ excluding the maximal set.

Let, $m$ denote the number of non-singlet elements in $B$ i.e., the number of linear equations as explained in (1.1) 
\bea
N &=& |B|-1 \nonumber \\
 &=& (n+1+m)-1 \nonumber  \\
 &=& n+m \nonumber
\eea
{\bf Number of facets = Number of linear equations + dimension of  gen permutahedron}

@@

(1) If $B$ consists of only singlets i.e., $B=\{ \{ 0,1,\cdots,n \}, \{ 0 \},\{ 1 \},\cdots ,\{ n \} \}$ then the generalised permutahedron is a Simplex. In this case the relevant $x$ variables are $x_i,~ i=0,\cdots,n$ with $x_0=1$ and $\sum_{i=0}^n x_i$. 
The Newton polytope of the Minkowski sum is $\prod_{i=1}^{n} x_i (1+\sum_{j=1}^{n} x_j)$ and $u$-variables are 
$u_i =\frac{ x_i}{1+\sum_{i=1}^n x_i} $
which satisfy $\sum u_i =1$ as their only $u$-equation. \\

(2) If $B= \{[i] | i=1,\cdots,n+1 \}$ is the complete flag of intervals, then ${\mathscr N_n}^y({\bf Y})$ is the Stanley-Pitman polytope or Hypercube.
The Newton polytope of the Minkowski sum is $x_1\cdots x_n (1+x_1) \cdots (1+x_1+\cdots +x_n)$ and $u$-variables are 
$u_i =\frac{ 1}{1+\sum_{j=1}^{i} x_j} $, ~~$u^{'}_i =\frac{ \sum_{j=1}^{i} x_j}{1+\sum_{j=1}^{i} x_j} $ for $j=1,\cdots,n$ \\
which satisfy $u_i +u^{'}_{i} =1$ as their $u$-equation. \\

(3) If $B$ corresponds to all the non empty subsets of $[0,n]$ and $Y_I =y_{|I|}$ i.e., the variables $Y_I$ are equal for all subsets of the same cardinality, then ${\mathscr N_n}({\bf Y})$ is the usual permutahedron $P_n$. \\

(4)If $B=\{ [i,j] | 1\leq  i \leq j \leq n\}$ is the set of consecutive intervals, then ${\mathscr N_n}({\bf Y})$ is the associahedron. \\

(5) If $B=\{ [1,i] \cup [j,n] | 1\leq  i \leq j \leq n\}$ is the set of cyclic intervals, then ${\mathscr N_n}({\bf Y})$ is the Cyclohedron.\\

(6) Let $\Gamma$ be a graph on the vertex set $[0,n]$. Let us assume that $B = B(\Gamma)$ is the set of subsets $I \in [n]$ such that the induced graph $\Gamma$ is connected, then  ${\mathscr N_n}({\bf Y})$ is a graph associahedron.\\

\section*{Braid arrangement}
The braid arrangement in $\mathbb{R}^{n+1}$ consists of $\left({n}\atop{2}\right)$ hyperplanes 
\bea
z_i =z_j ~~{\rm for ~ all}~~0 \leq i<j \leq n
\eea 
\subsection{Natural stringy integrals with linear factors}

@@

Within all generalized permutahedrons, the original permutahedron is quite simple
and important because any other generalized permutahedron can be degenerated from
permutahedron by setting some $S_I$ to be zero.
The building set of the $n$-dimensional permutahedron $\mathscr P_n$ is 
the set of all non-empty subsets of $[0,n]$. AHBY conditions can be solved from 
eq.\eqref{GPfacet}
\[
	S_I = (-1)^{|I|+1}\sum_{i\in I} S_i,
\]
for all non-empty subsets $I \subset [0,n]$ which are not singlets.
To get $u$-equations, we should solve $S_J$ by $F_J$ from eq.\eqref{GPfacet}, the 
solution for permutahedron $\mathscr P_n$ is 
\begin{equation}\label{SinF}
	S_I=\sum_{J\neq \varnothing,J\subset I} (-1)^{|J|-|I|}F_J,
\end{equation}
then
\[
	\prod_{I\neq \varnothing,I\subset [0,n]}u_I^{F_I}=
	\prod_{I\neq \varnothing,I\subset [0,n]}x_I^{S_I}=
	\prod_{\varnothing\neq J\subset I\subset [0,n]}
	x_I^{(-1)^{|J|-|I|}F_J}=
	\prod_{J\neq \varnothing,J\subset [0,n]}
	\prod_{I\supset J}(x_I^{(-1)^{|J|-|I|}})^{F_J}
\]
gives that
\[
	u_I=\prod_{J\supset I}x_J^{(-1)^{|I|-|J|}}.
\]
For example, the $u$-variables of $\mathscr P_2$ are
\[
	u_{1}  = \frac{x_1 x_{123}}{x_{12}x_{13}},\quad 
	u_{2}  = \frac{x_2 x_{123}}{x_{12}x_{23}},\quad
	u_{3}  = \frac{x_3 x_{123}}{x_{13}x_{23}},\quad
	u_{12} = \frac{x_{12}}{x_{123}},\quad 
	u_{13} = \frac{x_{13}}{x_{123}},\quad
	u_{23} = \frac{x_{23}}{x_{123}}.
\]
They satisfy the following equations
\begin{align*}
	&1-u_{1}=u_{2} u_{3} u_{23}^2,
	1-u_{2}=u_{1} u_{3} u_{13}^2,
	1-u_{3}=u_{1} u_{2} u_{12}^2,\\
	&1-u_{12}=u_{3} u_{13} u_{23},
	1-u_{13}=u_{2} u_{12} u_{23},
	1-u_{23}=u_{1} u_{12} u_{13}.
\end{align*}
We will discuss these $u$-equations in the next subsection.

@@

{\bf argue in general to have binary geometries we must have $1-u=\prod u' p(\{u\})$ with $p(u=0)=1$, conjecture that this is true of ALL gen. perm. Show it for gen. perm. more examples?}

@@

In the above, we have shown that the binary geometries exist for permutohedra even through the $u$ equtions are not perfect and conjecture that such binary geometries exist for generalized permutohedra. In the remainder of this section, we will give more example on such binary geometries without perfect $u$ equations.

@@

the $u$ variables are 
\begin{align}
   &u_{1}=\frac{x_{1}x_{123}}{x_{12}x_{13}} \:, \quad  u_{2}=\frac{x_{2}x_{123}}{x_{12}x_{23}} \:,  \quad 
   u_{3}=\frac{x_{3}x_{134}x_{234}x_{123}}{x_{34}x_{13}x_{23}x_{1234}} \:, \quad 
   u_{4}=\frac{x_{4}}{x_{34}} \\
   &u_{12}=\frac{x_{12}}{x_{123}} \:, \quad u_{13}=\frac{x_{13}x_{1234}}{x_{134}x_{123}} \:,\quad 
   u_{23}=\frac{x_{23}x_{1234}}{x_{123}x_{234}} \:, \quad u_{34}=\frac{x_{34}x_{1234}}{x_{134}x_{234}} \\
   &u_{123}=\frac{x_{123}}{x_{1234}} \:, \quad u_{134}=\frac{x_{134}}{x_{1234}} \:, \quad 
   u_{234}=\frac{x_{234}}{x_{1234}}
\end{align}
The $u$ equations are
\begin{align}
   &1-u_{1}=u_{2}u_{3}u_{23}^{2}u_{34}u_{234}^{2} \:, \\
   &1-u_{2}=u_{1}u_{3}u_{13}^{2}u_{34}u_{123}^{2} \:, \\
   &1-u_{3}= u_{1}u_{2}u_{4}u_{12}^{2}(1+u_{3}u_{13}u_{23}u_{34}u_{123}u_{134}u_{234}) \:, \\
   &1-u_{4}=u_{3}u_{13}u_{23}u_{123}  \:, \\
   &1-u_{12} =u_{3}u_{13}u_{23}u_{34}u_{134}u_{234} \:, \\
   &1-u_{13} =u_{2}u_{4}u_{12}u_{23}u_{34}u_{234}^{2} \:, \\
   &1-u_{23}= u_{1}u_{4}u_{12}u_{13}u_{34}u_{134}^{2} \:, \\
   &1-u_{34}= u_{1}u_{2}u_{12}^{2}u_{13}u_{23}u_{123}^{2} \:, \\
   &1-u_{123}=u_{4}u_{34}u_{134}u_{234} \:, \\
   &1-u_{134}=u_{2}u_{12}u_{23}u_{123}u_{234} \:, \\
   &1-u_{234}=u_{1}u_{12}u_{13}u_{123}u_{134} \:, 
\end{align} 
\subsection{Permutahedron as a binary geometry}
In this section we shall try to argue that the permutahedron is a binary geometry. We shall first summarise the following facts about the permutahedron from our discussion in the earlier sections:
\begin{enumerate}
\item The $u$-variables for the permutahedron are: 
\bea
u_J &=& ~~\prod_{J \subset I} x_I^{(-1)^{|I|-|J|}} \nonumber \\
u^{'}_J &=& \prod_{{0 \in I}\atop{ \{0,\cdots,n\} - I \subset J}} x_I^{(-1)^{|I|-|J|+mod(n, 2)}} \nonumber
\eea
From above it is evident that $u^{'}_{I} = u_{\bar{I}} $ where $\bar{I}=[0,n]-I$ for all subsets $I$ that do not contain $0$. And the $2^{n+1}-2$ facets corresponding to proper subsets of $[0,n]$ correspond to the two copies of the $2^{n}-1$ non-empty subsets of $[1,n]$.

\item From the definition of the permutahedron as a Nestohedron we know that $I$ and $J$ are :

{\bf compatible if} $I\cap J = \emptyset$ or $I\cap J \neq \emptyset$ and either $I \subset J$ or $J \subset I$

{\bf incompatible if}   $I\cap J \neq \emptyset$ or $I\cap J = \emptyset$ and neither $I \not\subset J$ or $J \not\subset I$

Thus, each $u_I$ is compatible with itself and incompatible with $u^{'}_I$.

\item  Since, the permutahedron is permutation invariant in all $x_i$'s this should be reflected at the level of $u$'s and all $u_I$ and $u^{'}_{J}$ with the same $|I|$ and $|J| =n-|I|$ should have similar $u$-equations. We see that this is indeed the case :

Some of the $u$-equations for the $n$-dimensional permutahderon:\\

\bea
1-u_{I}= u_i u_j u^{2}_{ij} \prod_{J \subset I} u_{J \cup \{i\}} u_{J \cup \{j\}} u^{2}_{J \cup \{i,j\}} \prod_{K \subset S-I} (u^{'}_K)^{3} (u^{'}_{K \cup \{i\}})^{2}  (u^{'}_{K \cup\{j\}})^{2}  u^{'}_{K\cup \{i,j\}} \left( 1+ u^{'}_i u^{'}_j u^{'}_{ij} \prod_{I \subset L} u_L \right)                       \nonumber
\eea

The other $u$-equations are not two or three term equations and seem to be polynomials of order $|I|=n-2$ in the corresponding $u$'s.Thus, the most general $u$-equations can be conjectured to be:
\bea
1-u_{I} = \prod_{J} u^{s_J}_{J} P_{|I|}(u_I, u_J,u_K) 
\eea
where, $J$ are all sets incompatible with $I$

 $K$ are all sets compatible with $I$ excluding itself

  $s_J$ are positive integers. 
\end{enumerate}
We shall now try to argue ${\mathscr P_n}$ is binary. We proceed inductively by first noticing that 
\section{Configuration spaces with perfect $u$-equations from degenerating $A_n$ and $B_n$}
In this section we shall consider some degenerations of $A_n$ and $B_n$ and show that these form an infinite class of examples of binary geometries with perfect $u$-equations. To do this we shall use the fact that both $A_n$ and $B_n$ are generalised permutahedra and can be realised as a Minkowski sum of coordinate simplices.

@@

*******************
\subsection*{Degenerations which lead to products}
In this section we provide an answer to the question of which degenerations of $A_n$ and $B_n$ give the most general products of such geometries. We begin by stating the following results about Nestohedra.

The maximal set of a building set $B_{max}$ is the set of all inclusion maximal elements of the building set $B$. A building set $B$ is connected if $B_{max}$ has a single element.

{\bf Theorem:}If $B_1, B_2,\cdots B_n$ are connected subsets of a building set $B$ then the corresponding nestohedron ${\mathscr N_B}$ is isomorphic to the product of the nestohedra ${\mathscr N}_{ B_1} \times{\mathscr N}_{ B_2} \cdots \times {\mathscr N}_{B_n}$.
